Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-04-14 paper/main.tex
update refs
update acks

\myparagraph{Reproducibility} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
%  \vspace*{-1em}
\begin{acks}
%\paragraph*{Acknowledgements.} Blind
We would like to thank Hao Wang (Leiden University) for pointing us to the arguments of
\citep{EriPeaGar2019scalable}.
%
\manuel{}{: We should also thank the COST ACTION}
%
M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government. 
%Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
  %   Scientists' Support Program}.
\end{acks}

@@

\bibliographystyle{ACM-Reference-Format-abbrv}
\bibliography{optbib/abbrev,optbib/authors,optbib/abbrevshort,optbib/journals,optbib/biblio,optbib/crossref}%,./mendeley}

>>>>

\myparagraph{Reproducibility} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
%  \vspace*{-1em}
\begin{acks}
%\paragraph*{Acknowledgements.} Blind
We would like to thank Hao Wang (Leiden University) for pointing us to the arguments of
\citep{EriPeaGar2019scalable}.
%
This article is based upon work from COST Action CA15140 `Improving Applicability of Nature-Inspired Optimisation by Joining Theory and Practice (ImAppNIO)' supported by COST (European Cooperation in Science and Technology).
%
M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government. 
%Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
  % supported by the \grantsponsor{GS501100001809}{National Natural
  %   Science Foundation of
  %   China}{http://dx.doi.org/10.13039/501100001809} under Grant
  % No.:~\grantnum{GS501100001809}{61273304}
  % and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
  %   Scientists' Support Program}.
\end{acks}

@@

\bibliographystyle{ACM-Reference-Format-abbrv}
\bibliography{optbib/abbrev,optbib/authors,optbib/journals,optbib/biblio,optbib/crossref}%,./mendeley}
